\pdftitle

### 2018-12-17 maxNt_v4.tex
update paper

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-07-26T21:05:58+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

We hurry to say that the description just given is just \emph{one} way to
quantify and characterize cooperativity and functional grouping, not
\emph{the only} way. It can surely be criticized from many points of view.
Yet, it is quantitative and bears a more precise meaning than an undefined,
vague notion of \enquote{cooperativity}. Two persons who apply this
procedure to the same data will obtain the same numbers. Different
protocols can be based on the \me\ method, for instance protocols that take
into account the activities or pair activities of specific neurons rather
than population averages, or even protocols that take into account time
dependence.

The purpose of the present work is not to assess the merits of \me\ methods
with respect to other methods. Its main purpose is to show that there is a
problem in the way the \me\ method itself, as sketched above, is applied to
the activity of the recorded neurons. We believe that this problem is at
the root of some quirks about this method that were pointed out in the
literature \cite{roudietal2009b}. This problems extends also to more
complex versions of the method, possibly except versions that use
\enquote{hidden} neurons
\cite{smolensky1986,kulkarnietal2007,huang2015,dunnetal2017}. The problem is
that the recorded neurons are a \emph{sample} from a larger, unrecorded
population, but the \me\ method as applied above is treating them as
isolated from the rest of the brain. Hence, the results it provides cannot
be rightfully extrapolated. We will give a mathematical proof of this. Let
us first analyse this issue in more detail.

@@

We need to make an initial probability assignment for the state of the full
population before any experimental observations are made. This initial
assignment will be modified by our experimental observations, and these can
involve just a sample of the population. Our state of knowledge and initial
probability assignment should reflect that samples are somehow
representative of the whole population.

In this state of knowledge, denoted $\yH$, we know that the neurons in the
population are biologically or functionally similar, for example in
morphology or the kind of input or output they receive or give. But we are
completely ignorant about the physical details of the individual neurons.
Our ignorance is therefore symmetric under permutations of neuron
identities. This ignorance is represented by a probability distribution
that is symmetric under permutations of neuron identities; such a
distribution is usually called \emph{finitely exchangeable}
\cites{ericson1969}[\chap~1]{ghoshetal1997}. We stress that this
probability assignment is just an expression of the symmetry of our
\emph{ignorance} about the state of the population, not an expression of
some biologic or physical symmetry or identity of the neurons.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-09-13T14:10:47+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

% We hurry to say that the description just given is just \emph{one} way to
% quantify and characterize cooperativity and functional grouping, not
% \emph{the only} way. It can surely be criticized from many points of view.
% Yet, it is quantitative and bears a more precise meaning than an undefined,
% vague notion of \enquote{cooperativity}. Two persons who apply this
% procedure to the same data will obtain the same numbers. Different
% protocols can be based on the \me\ method, for instance protocols that take
% into account the activities or pair activities of specific neurons rather
% than population averages, or even protocols that take into account time
% dependence.

The purpose of the present work is to show that there is a problem in the
way the \me\ method itself, as sketched above, is applied to the activity
of the recorded neurons. We believe that this problem is at the root of
some quirks about this method that were pointed out in the literature
\cite{roudietal2009b}. This problems extends also to more complex versions
of the method, possibly except versions that use \enquote{hidden} neurons
\cite{smolensky1986,kulkarnietal2007,huang2015,dunnetal2017}. The problem
is that the recorded neurons are a \emph{sample} from a larger, unrecorded
population, but the \me\ method as applied above is treating them as
isolated from the rest of the brain. Hence, the results it provides cannot
be rightfully extrapolated. We will give a mathematical proof of this. Let
us first analyse this issue in more detail.

@@

%% from Yasser:
** we want to describe average activities so our initial knowledge
disregards details

** we assume sample is representative of full population, so our initial
knowledge is symmetric

\mynote{modidy this}We need to make an initial probability assignment for the state of the full
population before any experimental observations are made. This initial
assignment will be modified by our experimental observations, and these can
involve just a sample of the population. Our state of knowledge and initial
probability assignment should reflect that samples are somehow
representative of the whole population.

% In this state of knowledge, denoted $\yH$, we know that the neurons in the
% population are biologically or functionally similar, for example in
% morphology or the kind of input or output they receive or give. But we are
% completely ignorant about the physical details of the individual neurons.
We as
Our ignorance is therefore symmetric under permutations of neuron
identities. This ignorance is represented by a probability distribution
that is symmetric under permutations of neuron identities; such a
distribution is usually called \emph{finitely exchangeable}
\cites{ericson1969}[\chap~1]{ghoshetal1997}. We stress that this
probability assignment is just an expression of the symmetry of our
\emph{ignorance} about the state of the population, not an expression of
some biologic or physical symmetry or identity of the neurons.
